A Large-Scale Study of the Use of Eval in R

### 2020-08-28 inst/paper/main.tex
Updated corpus
comment

\begin{figure*}[!tb]\centering\includegraphics[width=\linewidth]
{pipeline.pdf}\caption{Pipeline}\label{fig:pipeline}
\end{figure*}

@@

%Unlike Javascript, R packages also call native code for access to efficient
%numerical and statistical routines. We intercept all calls to R functions and
%native functions from the programs and \eval calls. In the whole corpus there
%are \AllClosureCallCount calls to R functions and \AllNativeCallCount to native
%code. Of those, \eval contribute to only \EvalClosureCallCount calls to R
%functions and \EvalNativeCallCount to native code.

>>>>

\begin{figure*}[!tb]\centering\includegraphics[width=\linewidth]
{pipeline.pdf}\caption{Pipeline}label{fig:pipeline}
\end{figure*}

@@

##Unlike Javascript, R packages also call native code for access to efficient
##numerical and statistical routines. We intercept all calls to R functions and
##native functions from the programs and \eval calls. In the whole corpus there
##are \AllClosureCallCount calls to R functions and \AllNativeCallCount to native
##code. Of those, \eval contribute to only \EvalClosureCallCount calls to R
##functions and \EvalNativeCallCount to native code.
##
##\begin{table}[ht]\resizebox{\columnwidth}{!}{%
##    \begin{tabular}{lll}\hline
##      Source & Primitive Functions & R Functions & Native Functions \\ \hline
##      Core & \CorePrimitiveFunctionCount & \CoreRFunctionCount & \CoreNativeFunctionCount \\
##      CRAN & \PackagePrimitiveFunctionCount & \PackageRFunctionCount & \PackageNativeFunctionCount \\
##      All  & \AllPrimitiveFunctionCount & \AllRFunctionCount & \AllNativeFunctionCount \\
##    \end{tabular}} \label{table:operation-distribution}
##  \caption{Distribution of operation calls to \eval calls across Core and Package}
##\end{table}
